Piecewise Regression for Nutritional Outcomes Pre- and Post-CFTR Modulator

### 2022-05-19 StatNet/knot_models.qmd
Update knot_models.qmd

-   The `mcp` package provides an easy interface for fitting Bayesian regression models with multiple change points.
    -   Essentially it translates `lme4` syntax into JAGS.
-   Uninformative "t-tail" priors are used unless the user specifies something else.
    -   "The default priors should be suitable for estimation in the absence of strong prior knowledge."[@lindelovMcpPackageRegression2020a]

@@

-   `mcp` can model joined slopes with varying change points:

```{r}
#| echo: true
# Define the model
model = list(
  Vitamin.D ~ 1 + Time, # intercept + slope
  ~ 0 + Time,  # joined slope
  1 + (1|Patient.ID) ~ 0 + Time
)
```

@@

-   This looks terrible!

@@

-   Try a random slope
-   Apply similar models to other outcomes like sweat electrolytes, etc.

@@

    -   Large change in slope after second modulator start is likely driven by a few influential observations.

>>>>

-   The `mcp` package provides an easy interface for fitting Bayesian regression models with multiple change points.

    -   Essentially it translates `lme4` syntax into JAGS.

-   Uninformative "t-tail" priors are used unless the user specifies something else.

    -   "The default priors should be suitable for estimation in the absence of strong prior knowledge."[@lindelovMcpPackageRegression2020a]
    -   "Based on data to ensure that they remain uninformative across any order of magnitude." [@lindelovMcpPackageRegression2020a]

-   Intercept priors are t(0, 3\*sd(y), 3)

-   Slope priors are t(0, sd(y)/(max(x) − min(x)), 3).

-   The prior $\sigma$ is N(0, sd(y)).

-   U(−1, 1) prior is used on autoregressive coefficients.

@@

-   `mcp` can model joined slopes with varying change points.
-   Package documentation recommends Dirichlet priors, but they sample slowly.
    -   A multivariate generalization of the beta distribution, indexed by $\alpha$ ($\alpha$ = 1 is flat).
    -   The conjugate prior of the categorical distribution and multinomial distribution.

```{r}
#| echo: true
# Define the model
model = list(
  Vitamin.D ~ 1 + Time, # intercept + slope
  ~ 0 + Time,  # joined slope
  1 + (1|Patient.ID) ~ 0 + Time
)
priors = list(
  cp_1 = "dirichlet(1)"
)
```

@@

-   This looks terrible! `mcp` does seem to find a change point at time 0, but the change point at -3 doesn't make much sense.

@@

-   Apply similar models to other outcomes like sweat electrolytes, etc.
-   Look into frequentist approaches for automatic detection (`segmented` package, etc.)

@@

    -   Large change in slope after second modulator start is likely driven by a few influential observations.
    -   Posteriors may shrink towards priors too much if the data set is not large enough.
        -   The likelihood does not overwhelm the prior.
